Assessing primitives performance\\ on multi-stage \st{execution} implementations

### 2018-07-01 paper.tex
fix some todos

\title{Assessing primitives performance\\ on multi-stage execution \todo{modify maybe}}
%\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

@@

Virtual machines, besides the interpreter and just-in-time compiler optimization facilities, also include a set of primitive operations that the client language can use. Some of these are essential and cannot be performed in any other way. Others are optional: they can be expressed in the client language but are often implemented in the virtual machine to improve performance when the just-in-time compiler is unable to do so (start-up performance, speculative optimizations not implemented or not mature enough, etc.).

@@

\subsection{Methodology}
\todo{so now I have to figure out how to actually bootstrap errors computed that way}

@@

\subsection{Results} 
We performed the benchmarks upon five different string sizes: 0, 1, 5, 100 and 1000 characters. In the case of small strings, most of the time is spent activating the primitive and in the code before the main comparison loop, the primitive is performed with a little overall number of native instructions. In the case of large strings, the time spent executing the primitive is dominated by the main comparison loop. Figure~\ref{fig:bench} and Table \ref{tab:detail_bench} show the results in terms of relative speed-up towards the baseline implementation, respectively for \GCCLinux and \LLVMMac.

@@

\acks
\todo{add acknowledgments}
Acknowledgments, if needed.

>>>>

\title{Assessing primitives performance\\ on multi-stage \st{execution} implementations}
%\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

@@

\begin{abstract}
Virtual machines, besides the interpreter and just-in-time compiler optimization facilities, also include a set of primitive operations that the client language can use. Some of these are essential and cannot be performed in any other way. Others are optional: they can be expressed in the client language but are often implemented in the virtual machine to improve performance when the just-in-time compiler is unable to do so (start-up performance, speculative optimizations not implemented or not mature enough, etc.).

@@

\subsection{Methodology}

@@

\subsection{Results} 
We performed the benchmarks upon five different string sizes: 0, 1, 5, 100 and 1000 characters. In the case of small strings, most of the time is spent activating the primitive and in the code before the main comparison loop, the primitive is performed with a little overall number of native instructions. In the case of large strings, the time spent executing the primitive is dominated by the main comparison loop. Figure~\ref{fig:bench} and Table \ref{tab:detail_bench} show the results in terms of relative speed-up towards the baseline implementation, respectively for \GCCLinux and \LLVMMac.
The relative speed-up is obtained by dividing the baseline results by the execution times. Both the figure and the table shows bootstrapped standard errors. \todo{add ref for bootstrap ?}

@@

\acks
\todo{add acknowledgments}
Eliot, Levente
Acknowledgments, if needed.
